Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White Dwarf Progenitors

### 2018-12-05 paper/ms.tex
More work on Carlyn's paper.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}
Thermonuclear (Type Ia) supernovae (\SNeIa) are bright stellar explosions 
thought to occur when approximately 1.5 \Msun of material composed principally 
of C and O burns under degenerate conditions. This class of supernovae is
know to synthesize much of the Fe-group elements found in the galaxy and
the light curves of these events have a spectial property that allows
their use as distance indicators for cosmological studies~\citep{phillips:absolute}
resulting in the discovery of the acceleration of the expansion of
the Universe and thus the inference of Dark 
Energy~\citep{riess.filippenko.ea:observational,
perlmutter.aldering.ea:measurements,leibundgut2001}. 
This special property of the light curve is thought to follow
from the fact that the source of luminosity, the radioactive decay
of \Ni{56}, synthesized by the thermonuclear burning, is also the
principle source of opacity~\citep{Pinto2001The-type-Ia-sup}.

@@

The white dwarf merger progentor picture has two white dwarfs 
coming together and subsequently exploding~\citep{webbink84,ibentutukov84}.
This scenario provides an abundance of degenerate fuel, which may explain some 
bright events~\citep{scalzo:2010,Yuan:2010}. White dwarf mergers  scenario

The other main class of models is the DD progenitor,
\citep{webbink84,ibentutukov84}, in which two WDs inspiral and merge.
This scenario includes inspiraling pairs, collisions, violent mergers,
and also the ``core-degenerate'' model where the merger takes place in
a common envelope
\citep{raskinetal2009,pakmoretal2011,kashi:2011,pakmoretal2012a,Shenetal12}
Also
see~\citet{hillebrandt.niemeyer:type,howell2011,hillebrandtetal2013,calderetal2013}
for additional discussion.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}
Thermonuclear (Type Ia) supernovae (\SNeIa) are bright stellar explosions 
thought to occur when approximately 1.X \Msun of material composed principally 
of C and O burns under degenerate conditions (SETTLE ON X). This class of supernovae is
know to synthesize much of the Fe-group elements found in the galaxy and
the light curves of these events have a spectial property that allows
their use as distance indicators for cosmological studies~\citep{phillips:absolute}
resulting in the discovery of the acceleration of the expansion of
the Universe and thus the inference of Dark 
Energy~\citep{riess.filippenko.ea:observational,
perlmutter.aldering.ea:measurements,leibundgut2001}. 
This special property of the light curve is thought to follow
from the fact that the source of luminosity, the radioactive decay
of \Ni{56}, synthesized by the thermonuclear burning, is also the
principle source of opacity~\citep{Pinto2001The-type-Ia-sup}.

@@

The white dwarf merger progentor picture has two white dwarfs 
coming together and subsequently exploding~\citep{webbink84,ibentutukov84}.
This scenario provides an abundance of degenerate fuel, which may explain some 
bright events~\citep{scalzo:2010,Yuan:2010}. White dwarf mergers include
variations on the interaction and include

inspiraling pairs, collisions, violent mergers,
and the ``core-degenerate'' model where the merger takes place in
a common envelope
\citep{raskinetal2009,pakmoretal2011,kashi:2011,pakmoretal2012a,Shenetal12}
Also
see~\citet{hillebrandt.niemeyer:type,howell2011,hillebrandtetal2013,calderetal2013}
for additional discussion.
